---
title: "PSYC259_Assignment2"
author: "Amanda Mae Woodward"
date: "10/14/2020"
output: html_document
---
Complete the following questions for Assignment 2. Please upload your completed Assignment to GitHub classrooms as **R MarkDown Files**.

1. Create a vector called score that contains every 9th number between 1 and 109. 
```{r}
score<- seq(9,109, by=9)
score
```

2. Create a vector called participants that contains the numbers 1-12.
```{r}
participants<- 1:12
participants
```

3. Create a vector called condition that repeats the words control and experimental six times. 
```{r}
condition<- rep(c("control", "experimental"),6)
condition
```

4. Create a dataframe from the vectors in #1-3.
```{r}
dat<-cbind.data.frame( participants, condition,score)
dat
```

5. Take the mean of the score column.
```{r}
mean(dat$score)
```

6. Open the mtcars dataframe. Create a subset of data for cars that have 6 cylinders (cyl column).
```{r}
data(mtcars)
car<- subset(mtcars, mtcars$cyl==6)
```

7. Summarize this subset of data. 
```{r}
summary(car)
```

8. Create a dataframe that contains cars with higher than average miles per gallon (mpg). 
```{r}
goodMile<- mtcars[mtcars$mpg>mean(mtcars$mpg),]
```

9. How many cars are in this subset? 
```{r}
nrow(goodMile)
```

Challenge Questions: 
10. Open the diamonds dataset. Create a new dataframe that has diamonds greater than 1 carat and an ideal cut. Find the mean and standard deviation of price for this data. 
```{r}
library(ggplot2)
data(diamonds)
bigDiamond<- diamonds[diamonds$carat>1 & diamonds$cut=="Ideal",]
mean(bigDiamond$price)
sd(bigDiamond$price)
```

11. Create a new dataframe that includes all diamonds with a price between $2500 and $5000. Which color occurs most in this subset? 
```{r}
price<-diamonds[diamonds$price>2500 & diamonds$price<5000,]
summary(price$color)
```
F occurs most
