---
title: 'PSYC259: Quiz 1'
author: "Amanda Mae Woodward"
date: "10/17/2020"
output: html_document
---
Assignment: For this assignment, you will need to use the skills you have developed in the last two weeks. You **are** allowed to work with each other

**Pt 1**
1. Create a dataframe containing two columns: one with five desserts and one with your ratings of them.
```{r}
food<-c("iceCream", "cake", "brownies", "cookies", "other")
rating<- c(9,8,10,7,5)
dessert<- cbind.data.frame(food, rating)
```
2. What are the mean and standard deviation of your ratings? 
```{r}
mean(dessert$rating)
sd(dessert$rating)
```

3. Print just the row containing your highest ranked dessert. 
```{r}
dessert[3,]
```

**Part 2**
4. Create a function that indicates whether a number is even or odd.
```{r}
oddEvenTwo<-function(Num){
  ifelse(Num%%2==0,"even", "odd")
}
oddEvenTwo(19)
```
```{r}
oddEven<- function(Num){
  if(as.integer(Num/2)==TRUE){
    print("even")
}else{print("odd")}
}
```

5. Test your function by inputting the number 19,
```{r}
oddEven(19)
```

6. Create a vector containing the numbers 1 through 100.
```{r}
Vec<- 1:100
```

7. Modify your function to test whether all numbers in a vector are even or odd. (hint: this means you need to iterate through a list!) 
```{r}
"nrow- expects a dataframe"
nrow(as.data.frame(Vec))
length(Vec)


oddEven2(Vec)
for(i in Vec){
  print(oddEven(i))
}

```

8. Test your new function using the vector in #6. 
```{r}
oddEven2(Vec)
```

**Pt 3**
All questions will use the diamonds dataset (in the ggplot2 library).

9. Summarize the dataset.
```{r}
library(ggplot2)
data(diamonds)
```

10. What type of variable is cut? How do you know? 
```{r}
class(diamonds$cut)
```
it's an ordered factor- because i clicked "class and it told me". I couldve also found out using summary

11. What type of variable is price? How do you know?
```{r}
class(diamonds$price)
```
it's an integer. same reasoning as above

12. Create a subset of the dataset that contains all diamonds with a VS1 clarity. 
```{r}
dVS<- subset(diamonds, diamonds$clarity=="VS1")
```

13.How many diamonds are in this dataset? 
```{r}
nrow(dVS)
```

14. Add a column to this subset indicating whether a diamonds' carat is small (less than the first quartile), average (between the first and third quartile), or large (greater than the third quartile).
```{r}
a<-summary(dVS$carat)
str(a)
library(ggplot2)
data(diamonds)
dVS<- subset(diamonds, diamonds$clarity=="VS1")

dVS$size<-NA

for(i in 1:nrow(dVS)){
  if(dVS$carat[i]<0.38){
  dVS$size[i]<-"small"
  } 
  if(dVS$carat[i]>1.01){
    dVS$size[i]<- "large"
  } 
  if(dVS$carat[i]>0.38 & dVS$carat[i]<1.01){ dVS$size[i]<- "medium"}
}

```

