---
title: "PSYC259- DataManipulationAssignment"
author: "Amanda Mae Woodward"
date: "10/28/2020"
output: html_document
---

1.Open the sleep dataset in R 
```{r}
data(sleep)
```

2. Is it long or wide format? How do you know? 
long format- the subject id's repeat and each subject experiences both group 1 and group 2
3. Transform this data so that it is in the other format. 
```{r}
library(tidyr)
sleepWide<-pivot_wider(sleep,id_cols="ID", names_from= "group", values_from= "extra")
```

4. Transform your data back to its original format. 
```{r}
sleepLong<-pivot_longer(sleepWide,cols = c("1", "2"), names_to= "group", values_to= "extra")
```

5. Open the Starwars dataset
```{r}
data(starwars)
```

6. Create homeworld as a factor. How many levels does it have? 
```{r}
starwars$homeworld<-as.factor(starwars$homeworld)
levels(starwars$homeworld)
length(levels(starwars$homeworld))
```
48 levels

7. Reorder homeworld so that Naboo is the reference group. 
```{r}
starwars$homeworld<- relevel(starwars$homeworld, ref= "Naboo")
levels(starwars$homeworld)
```

8. Use mutate to create a column transforming kg to pounds. (hint: you may need to look up the conversion)
```{r}
dat<- starwars %>% 
  mutate(weightinPounds = mass/2.20462)
```

9. Print a summary of your column from #8
```{r}
dat %>% select(name, mass, weightinPounds)
summary(dat$weightinPounds)
```

